% resume.tex
%
% (c) 2011 Conan Chou <conanchou1412@gmail.com> (original author) http://mboedick.org
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[twoside,letterpaper,11pt]{article}
\usepackage{fancyhdr}
\usepackage{afterpage}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0pt}
\setlength{\headsep}{0pt}
\setlength{\textheight}{11in}
\setlength{\textheight}{10in}
\setlength{\topmargin}{-0.7in}
\setlength{\textwidth}{7.5in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}
%-----------------------------------------------------------
%\usepackage{fullpage}
%\usepackage{shading}
%\textheight=9.0in
%\pagestyle{fancy}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\usepackage[svgnames]{xcolor}
\usepackage{framed}
\definecolor{shadecolor}{gray}{0.85}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-5pt}}
% \newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\resheading}[1]{
  \parbox{\textwidth}{
    \begin{shaded}
      \textbf{\sffamily{\mbox{~}{\large #1} \vphantom{p\^{E}}}}
    \end{shaded}
  }\vspace{-6px}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

\begin{document}
\afterpage{\vspace*{12pt}}
\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Zhe ZHOU (Conan)}  & 917-822-3585\\
\#1682, 64TH ST, 2ND FL &  conanchou1412@gmail.com \\
Brooklyn, NY, 11204 & http://conanblog.me \& http://conanchou.github.com\\
\end{tabular*}
\\

\vspace{0in}
\resheading{Education}
\begin{description}
\item[Grade Point Average:]
\textbf{3.9/4.0}
\end{description}

\begin{itemize}
\item
	\ressubheading{Polytechnic Institute of New York University}{New York}{M.Sc., Computer Science}{2011 - 2013}
	\begin{itemize}
		\resitem{Relevant courses: Operating System, Algorithm, Computer Architecture, Artificial Intelligence, Machine Learning, Interactive Computer Graphics, Big Data Analysis and Management  etc.}
	\end{itemize}

\item
	\ressubheading{Singapore Management University}{Singapore}{B.Sc., 1\textsuperscript{st} major Info. Sys. Management; 2\textsuperscript{nd} major Advanced Business Solutions}{2006 - 2010}
	\begin{itemize}
		\resitem{Relevant courses: Enterprise Web Solution, Database Management, Computer Networks, Information Security, Enterprise Information System, etc.}
	\end{itemize}
\end{itemize}

\resheading{Skills}

\begin{description}
\item[Familiar with:]
C, Python, PHP, Java, SQL
\item[Basic Familiarity in:]
VB, C\#, Objective-C, ActionScript, JavaScript, HTML, CSS, MATLAB, \LaTeX, Common LISP
\item[Operating Systems:]
Linux (Debian, Ubuntu, OpenSUSE), Mac OS, Windows
%\item[Development Tools:]
%VIM, XCode, Eclipse, git, SVN, Adobe Photoshop, Adobe Fireworks
\end{description}

\resheading{Projects}
\begin{itemize}
\item
	\ressubheading{NewsFlashed.com}{NewsFlashed Inc.}{Designed the architecture, implemented a API crawler, and machine learning algorithms}{2012}
	\begin{itemize}
		\resitem{Description: Collecting and analysing user's interests for personalized news recommendation}
		\resitem{Technology: PHP, Python, C, node.js, mongoDB, MySQL, WordPress, Amazon EC2 and S3, etc.}
	\end{itemize}

%\item
%	\ressubheading{3D Sphere}{ICG course project}{Apply the computer graphic theories to the demo application from scratch}{2011}
%	\begin{itemize}
%		\resitem{Description: A demo application of modern interactive computer graphics}
%		\resitem{Technology: C, OpenGL}
%	\end{itemize}

\item
	\ressubheading{Ponon!}{Artlans}{Designed the game storyline and developed twitter integration part}{2010}
	\begin{itemize}
		\resitem{Description: Create a block falling game for iPhone / iPod Touch / iPad}
		\resitem{Technology: Objective-C, iOS API, Twitter API, etc.}
	\end{itemize}

\item 
	\ressubheading{Terrapin}{SMU IS Department}{Developed the automation script, Ajax, and Mantis integration
}{2009}
	\begin{itemize}
		\resitem{Description: Integrate the version controlling, bug tracker, and peer grouping and evaluation systems for auto course preparation}
		\resitem{Technology: Java, PHP, MySQL, bash, Apache, JavaScript, SVN, Mantis, etc.}
	\end{itemize}

\item
	\ressubheading{Xport}{Xtreme Coding 2008 Competition}{UI designer and developer}{2008}
	\begin{itemize}
		\resitem{Description: Develop a Adobe AIR app for extreme sports devotees to share videos, communicate, and plan events online}
		\resitem{Technology: Java, MySQL, Adobe AIR, Google Map API, Apache, etc.}
	\end{itemize}

\item
	\ressubheading{BVL 2.0}{Standard Chartered Bank}{Improved the business process and implemented the new design with the team}{2008}
	\begin{itemize}
		\resitem{Description: Build a internal knowledge sharing system for Standard Chartered Bank}
		\resitem{Technology: Microsoft SharePoint, C\#, .Net AJAX framework, JavaScript, etc.}
	\end{itemize}
%\item
%	\ressubheading{ByeSmoke}{Xtreme Coding 2007 Competition}{Lead developer}{2007}
%	\begin{itemize}
%		\resitem{Description: Develop a location based Android app to help smoker to abstain from smoking}
%		\resitem{Technology: Android, Java, Apache, MySQL, Twitter API}
%	\end{itemize}
\newpage
\thispagestyle{fancy}{
\fancyhead[C]{Zhe ZHOU :: 917-822-3585 :: conanchou1412@gmail.com :: \#1682, 64TH ST, 2ND FL, Brooklyn, NY, 11204}
}
\item
	\ressubheading{ezVET}{Pets Lover Club}{Implemented backend logic and the frontend for both desktop and mobile platform
}{2007}
	\begin{itemize}
		\resitem{Description: Build a platform providing a better solution for veterinarians to schedule and cooperate to serve their customers}
		\resitem{Technology: Java, MySQL, JavaScript, Google Gear and Map APIs, Android, SMS Web Service, etc.}
	\end{itemize}
\end{itemize}

\resheading{Pet Projects}
\begin{itemize}
\item
	\ressubheading{Infophile}{iOS}{in progress, not released yet}{2012}
	\begin{itemize}
		\resitem{Description: A iOS App and service for better personalized information retrieval.}
		\resitem{Technology: Objective-C, Python, Cassandra, Nginx}
	\end{itemize}
\item
	\ressubheading{Unix as IDE in Chinese}{Sphinx}{Open Source}{2012}
	\begin{itemize}
		\resitem{Description: Translation of a serial of article about using Unix as IDE.}
		\resitem{Technology: Sphinx}
		\resitem{URL: https://github.com/ConanChou/Unix-as-IDE--Chinese-}
	\end{itemize}
\item
	\ressubheading{wp-dropcaps}{Wordpress}{Open Source}{2011}
	\begin{itemize}
		\resitem{Description: A plugin for Wordpress to make drop-cap effect in the post.}
		\resitem{Technology: PHP, CSS}
		\resitem{URL: http://wordpress.org/extend/plugins/wp-dropcaps/}
	\end{itemize}

\item
	\ressubheading{rt2x}{Twitter}{Open Source}{2010}
	\begin{itemize}
		\resitem{Description: A plugin for TweetNest to forward tweets to other SNS like renren, sina, fanfou, renjian, and zuosha.}
		\resitem{Technology: PHP, MySQL}
		\resitem{URL: https://github.com/ConanChou/tweetnest-with-rt2x}
	\end{itemize}
\end{itemize}
\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{Lead developer and Architecture Designer (Intern)}{NewsFlashed Inc., US}{in charge of architecture design, crawler, and machine learning algorithms}{2012}
\item
	\ressubheading{Research Assistant on Cloud Security}{SMU, Singapore}{in charge of the experiments implementation and data analysis}{2010}
	\begin{itemize}
		\resitem{Project Paper: On Trustworthiness of CPU Usage Metering and Accounting}
	\end{itemize}

\item
	\ressubheading{Chief Technology Officer}{Artlans, China}{in charge of Research and Development}{2009 - 2010}

\item
	\ressubheading{Teaching Assistant of course Enterprise Web Solution}{SMU, Singapore}{in charge of the lab session}{2009}

\item
	\ressubheading{System Developer (Intern)}{Standard Chartered Bank Regional HQ, Singapore}{in charge of the feature implementation}{2008}

\item
	\ressubheading{IT Administrator (Part-time)}{Success Human Resource Center Pte Ltd, Singapore}{IT support and business solution consultant}{2007}

%\item
%	\ressubheading{Free writer}{Hacker X Files magazine, China}{Topics mainly focused on network security and software security}{2003 - 2005}
\end{itemize}

\resheading{Awards}
	\begin{tabular*}{7.4in}{l@{\extracolsep{\fill}}r}
		CS Department Scholarship & 2011, 2012\\
		Lee Kuan Yew Global Business Plan Competition the 4\textsuperscript{th} Place & 2008\\
		China the 6\textsuperscript{th} Challenge Cup Silver Award & 2008\\
\end{tabular*}

\end{document}